A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
size is beside the point, Comment 3
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1063 43ef1190-90fd-4dd7-a769-d0121f02b80e
Comment on RKBexplorer
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1064 43ef1190-90fd-4dd7-a769-d0121f02b80e

We make several approaches to ensure that we visit a large and
representative section of the open Semantic Web. We take SPARQL
Endpoints from the SPARQLES survey \cite{buil2013sparql}, vocabularies
from Linked Open Vocabularies (LOV) \cite{lov2} and prefix.cc, and
we augment these data with spidered data from the Billion Triple
Challenge (BTC) 2014 \cite{btc-2014} dataset.

@@

We also note that prohibition of SPARQL results caching is rare.
Amongst the servers that expose caching headers it is common
that the result may be cached for some minutes.

>>>>

We make several approaches to ensure that we visit a large and
representative section of the open Semantic Web. We take SPARQL
Endpoints from the SPARQLES survey \cite{buil2013sparql}, vocabularies
from Linked Open Vocabularies (LOV) \cite{lov2} and prefix.cc, and we
augment these data with spidered data from the Billion Triple
Challenge (BTC) 2014 \cite{btc-2014} dataset. Of these, BTC2014 is by
far the largest, the others are small, curated and targeted
datasets. However, the size is besides the point, we are only
interested in examining as many hosts as possible, and they are still
few.

@@

We also note that prohibition of SPARQL results caching is rare.
Amongst the servers that expose caching headers it is common
that the result may be cached for some minutes, and closer inspection
of the dataset reveals that many of these are due to that
RBKExplorer\footnote{\url{http://www.rkbexplorer.com/}} sets an
freshness lifetime of 300~s for many endpoints.
